
\section{Conclusion and perspectives}
\label{sec:conclusion}

\TODO{A lot to change. Includes perspective with security, maybe problems of
  merging etc.}

WebRTC opened a new playground for large-scale distributed applications
deployed on a network of browsers. Browsers as infrastructure ease the
deployment of large-scale distributed applications for end-users. As a core
component of many large-scale distributed applications, we pointed out current
peer-sampling protocols' limitations in term of adaptivity or reliability.

In this paper, we described \SPRAY, an adaptative-by-design random peer
sampling approach designed to fit the WebRTC constraints.  \SPRAY provides:
\begin{inparaenum}[(i)]
\item logarithmically growing partial views reflecting the global network size,
\item constant time complexity on connection establishments using solely
  neighbor-to-neighbor interactions,
% \item an exponentially fast convergence to an overlay network exposing
%   properties similar to random graphs.
\end{inparaenum}

% Synthesis of experiments
In experiments, we demonstrated how \SPRAY adaptiveness improves random peer
sampling performances when network size is changing. In particular, the average
shortest path length scales better, the in-degree evolves with the network
size, and it converges faster.  We also demonstrated that \SPRAY stays robust
to massive failures. \SPRAY and \CYCLON are quite similar when the network size
is optimal for \CYCLON. However, \SPRAY saves connections when \CYCLON is
oversized and is more robust when \CYCLON is undersized. Adaptiveness comes at
the price of duplicates in the partial views. However, the simulations
supported by theoretical analysis shows that the number of duplicates remains
very low and becomes negligible in large networks.


% As such, \SPRAY constitutes an improvement over state-of-the-art
% approaches in the traditional context of 1-way connection establishments. In
% addition, the improvement becomes crucial in the 3-way handshake connection
% set-up which is increasingly important since recent technologies (e.g. WebRTC)
% allow peer-to-peer connections between modern web browsers. Random peer
% sampling protocols constitute the ground of many decentralized applications.
% Thus, we expect that decentralized applications (requiring scalable broadcast
% among other) will flourish in the web browsers, while they were previously
% quartered to standalone applications.


Future work includes a Javascript implementation of \SPRAY. An in-browser
implementation opens the gate to emulations, and even real peer-to-peer
distributed and decentralized applications.

Future work also includes investigations on topology managers such as
T-Man~\cite{jelasity2009tman} or
Vicinity~\cite{voulgaris2005epidemic}. Indeed, they traditionally rely
on random peer sampling approaches using fixed-size partial
view. Thus, they maintain a fixed-size view of their most closely
related neighbors using a ranking function. With \SPRAY, it is
possible to extend their behavior to use dynamic partial views. If
the view size could adapt to the size of a cluster (e.g. if the topology
creates disjoint clusters), it would improve the traffic, robustness,
etc.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:
