
\section{Problem statement}

We consider a set $V$ of peers labeled from $p_1$ to $p_N$.  The peers can
crash or leave at any time without giving notice, and they can recover or
re-enter the network freely. We consider only non-byzantine peers.

A multiset of arcs $E = (p_f,\,p_t) \in V \times V$ allows $p_f$ to communicate
with $p_t$ but not the converse. The multiset of arcs is dynamic, i.e., arcs
appear and disappear over time. The network $\mathcal{N}^t \in V \times E$ is a
\emph{network overlay} at the given time $t$.

The multiset of arcs starting from $p_f$ is called the \emph{partial view} of
$p_f$, noted $\mathcal{P}_f$. The destination peers in this view are the
\emph{neighbors} of $p_f$. A partial view can contain arcs that are stale when
the neighbor has left or crashed.

The peers communicate by the mean of messages. They only send messages to their
neighbors. A departed peer cannot send messages. An arc can fail to deliver a
message. A stale arc systematically fails.

Building an adaptive-by-design random peer sampling that meets WebRTC
constraints raises the following scientific problem:
\begin{problem}
  Let $t$ be an arbitrary time frame, let $V^t$ be the network membership at
  that given time $t$ and let $\mathcal{P}_x^t$ be the partial view of peer
  $p_x \in \mathcal{V}^t$.  An efficient random peer sampling should provide
  the following properties:
  \begin{enumerate}
  \item Partial view size: \hfill
    $\forall p_x \in V^t,\, |\mathcal{P}_x^t| = \mathcal{O} (\ln
    |V^t|)$      
  \item Connection establishment: \hfill $\mathcal{O}(1)$
    %% \item  \begin{center}
    %%     Convergence speed: \hfill $\Theta(\exp \, t^{-1})$
    %%   \end{center}
  \end{enumerate}
\end{problem}

The first condition states that the partial view size is relative to the size of
the network at any time. It also states that partial views should grow and
shrink, at worst, logarithmically compared to the size of the network. The
second condition states that each connection establishment requires a constant
number of intermediary peers. Since this number is constant, connection
establishments do not depend on the network size.
%% The last condition states that the network
%% overlay converges exponentially fast to a topology that is close to a random
%% graph.
Lpbcast, HyParView, Newscast, and \CYCLON fail to meet the first condition of
the problem statement since they do not adapt their views to the network
size. \SCAMP fails to meet the second condition of the problem statement since
each connection implies an unsafe random dissemination. The next session
introduces \SPRAY that meets both of these constraints without any global
knowledge.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:
